---
title: "T-Test Problem"
author: "Jennifer Dimmett"
date: "Spring, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
Ourdata <- read.csv(file="GSScsv.csv")
library(ggplot2)
```


## Is there a difference in  average years of education (EDUC) between the those who did or did not vote in 2012 (VOTE12)?

$H_0$ : No difference between average years of education between those who voted and those who did not vote in 2012  

$H_A$ : There is a difference in the average years of education between those who voted in 2012 and those who did not. 

## Graphical Summary  

```{r}
plot(EDUC~VOTE12, data=Ourdata, 
     xlab="Voting 2012",
     ylab="Years of Education",
     main="Education vs Voting 2012")
```



Graph illustrates that the group with more education has input on voting



## numerical summary

```{r}
favstats(EDUC~VOTE12,data=Ourdata)
```

Numerical summary shows a difference.


## inferential test 


```{r}
t.test(EDUC ~ VOTE12, data=Ourdata)
```

##  Conclusion

P < 0.005, so we reject the null hypothesis and conclude we have evidence that there is a difference between the average years of education of those who voted in 2012 and those who did not vote in 2012.